Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Clean up paragraph in introduction

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions are caused by Reynolds number effects, other turbine
parameters or issues with the numerical model. One might also obtain different
predictions of scaled systems due to modified physics at lower Reynolds numbers,
e.g., laminar boundary layers and transitional flow regimes. If the numerical
model is then considered ``validated,'' there is a risk that its application at
full-scale may produce incorrect predictions. It is uncertain whether numerical
models validated with physical model data obtained at low Reynolds number should
be considered validated at all, since the scale at which the model will be
applied is orders of magnitude larger.

>>>>

If numerical models are validated with physical model data that was obtained at
insufficiently high Reynolds numbers, it cannot be determined whether problems
with model predictions are caused by Reynolds number effects, other turbine
parameters or issues with the numerical model itself. One might also obtain
different predictions of scaled systems due to modified physics at lower
Reynolds numbers, e.g., laminar boundary layers and transitional flow regimes.
If the numerical model is then considered ``validated,'' there is a risk that
its application at full-scale may produce incorrect predictions. As such, it is
questionable whether numerical models validated with physical model data
obtained at Reynolds numbers orders of magnitude away from prototype scale
should be considered validated at all.
